Automatic extraction of symbolic network signatures from malware code

### 2016-10-10 paper.tex
finished proposal

%opening
\title{Automatic extraction of network signatures from malware code}
\author{Arjun Gurumurthy, Kausik Subramanian}

@@

\begin{abstract}

\end{abstract}

@@

\section{Challenges}
We abstract the problem to the following: given a program point,
can we automatically provide an ordered set of symbolic packets 
that must be received (and sent) by the client such that the program 
reaches the program point. The symbolic packets can be used as
network signatures and used to detect malware (a set of packets
satisfying the symbolic packets in order will infer that there 
is a malware with high confidence). By constructing symbolic packet
signatures, we can generalise the intrusion policy and reduce 
true negatives.

\bibliographystyle{abbrv}
\bibliography{references}

>>>>

%opening
\title{Automatic extraction of symbolic network signatures from malware code}
\author{Arjun Gurumurthy, Kausik Subramanian}

@@

\begin{abstract}
We propose the automatic extraction of symbolic network signatures from malware code to aid and automate network-based malware detection systems.
\end{abstract}

@@

\section{Challenges}
We abstract the problem to the following: given a program point,
can we automatically provide an ordered set of symbolic packets 
that must be received (and sent) by the client such that the program 
reaches the program point. The symbolic packets can be used as
network signatures and used to detect malware (a set of packets
satisfying the symbolic packets in order will infer that there 
is a malware with high confidence). By constructing symbolic packet
signatures, we can generalise the intrusion policy and reduce 
true negatives (thus not affecting legitimate traffic).

Malware code can be thought of as a program reacting based on input received
packets received (possibly multi-threaded), which
could require changes to existing reachability analyses tools 
like Codesurfer~\cite{codesurfer}. To extract symbolic network
signatures, we need to define the abstract semantics of the program
suited for network signatures, and define the \emph{combine} and 
\emph{extend} operators used for interprocedural analysis.

\section{Project Proposal}
\textbf{Tasks}:
\begin{itemize}
	\item Identify and characterize features of common malware code - 1-2 weeks
	\item Develop the abstract semantics and operators for extracting  
	symbolic network signatures from malware code - 2-3 weeks
	\item Modifying/Extending existing tools like Codesurfer for symbolic 
	network signature extraction - 2-3 weeks
\end{itemize}

\noindent\textbf{Open source tools}: Static analysis tools, malware repositories

\noindent\textbf{Evaluation}: 
The primary metrics of evaluation are time taken for analysis, accuracy and 
generality of the symbolic signatures. Performance analysis can be performed 
with different malware programs with varying lines of code to understand
the time complexity of the analysis. The quality of the symbolic network
signatures is a tougher metric to measure. Ideally, the symbolic network 
signature must only include packets which will make the program reach the
specified point. If the signature is more general, legitimate packets may 
be considered as malicious and blocked. On the other hand, the signature
may miss actual malware traffic because the signature does not encompass
all inputs leading to the point. We would try to address these trade-offs in
our evaluation.
\bibliographystyle{abbrv}
\bibliography{references}
